% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}

\documentclass[]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
  \usepackage{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
  \usepackage[left=2.5in,bottom=1.25in,top=1.25in,right=1in]{geometry}
  \ifxetex
\usepackage[setpagesize=false, % page size defined by xetex
            unicode=false, % unicode breaks when used with xetex
            xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
bookmarks=true,
pdfauthor={},
pdftitle={My preregistration for AsPredicted.org},
colorlinks=true,
citecolor=blue,
urlcolor=blue,
linkcolor=magenta,
pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% Customization for cos_prereg
\usepackage{longtable,booktabs,threeparttable,tabularx}
\linespread{1.5}
\newcounter{question}
\setcounter{question}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\setlength{\droptitle}{-2em}
\title{My preregistration for AsPredicted.org}
\pretitle{\begin{changemargin}{-8pc}{0pc} \centering\large Preregistration\\ \Huge}
\posttitle{\end{changemargin}}
  \author{
          First Author\textsuperscript{1},
          Ernst-August
Doelle\textsuperscript{1,2}          \\ \vspace{0.5cm}
              \textsuperscript{1} Wilhelm-Wundt-University\\
              \textsuperscript{2} Konstanz Business School      }

  \def\affdep{{"", ""}}%
  \def\affcity{{"", ""}}%
  \preauthor{\begin{changemargin}{-8pc}{0pc} \centering\large}
  \postauthor{\end{changemargin}}
\date{02. October 2024}
\predate{\begin{changemargin}{-8pc}{0pc} \centering\large\emph}
\postdate{\end{changemargin}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{14.0pt}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{\large\textsc{\MakeLowercase{My preregistration}}}



% Title settings
\usepackage{titlesec}
\titleformat{\section}[display]{\bfseries\Large}{\thesection}{}{}[]
\titlespacing{\section}{0pc}{*3}{*1.5}
\titleformat{\subsection}[leftmargin]{\titlerule\bfseries\filleft}{\thesubsection}{.5em}{}
\titlespacing{\subsection}{8pc}{5ex plus .1ex minus .2ex}{1.5pc}


% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi


\begin{document}
\maketitle
\vspace{2pc}


\ifPDFTeX
  \newcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\else % if luatex or xetex
  \NewCommandCopy{\oldQuestion}{\Question}
  \renewcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}
\fi



\newcommand\Answer[1]{%
    \noindent
    \textit{Registered response}: #1\par}

\hypertarget{data-collection}{%
\subsection{Data collection}\label{data-collection}}

\textbf{Yes}, we already collected the data.

\textbf{No}, no data have been collected for this study yet.

\textbf{It's complicated.} We have already collected some data but
explain in Question 8 why readers may consider this a valid
\textbf{pre}-registration nevertheless.

\hypertarget{hypothesis}{%
\subsection{Hypothesis}\label{hypothesis}}

\begin{quote}
Example: A month-long academic summer program for disadvantaged kids
will reduce the drop in academic performance that occurs during the
summer.
\end{quote}

\hypertarget{dependent-variable}{%
\subsection{Dependent variable}\label{dependent-variable}}

\begin{quote}
Example: Simple average GPA across all courses during the first semester
after the intervention.
\end{quote}

\hypertarget{conditions}{%
\subsection{Conditions}\label{conditions}}

\begin{quote}
Example 1: Two conditions: Offering summer program: yes vs no.
\end{quote}

\begin{quote}
Example 2: 12 conditions in a mixed design lab study. Participants will
be assigned to one of four conditions: math training, verbal training,
memory task, or control (4 between-subject conditions). Each participant
will complete a math test, a verbal test, and a memory test (3
within-subject conditions).
\end{quote}

\hypertarget{analyses}{%
\subsection{Analyses}\label{analyses}}

\begin{quote}
Example: Linear regression predicting the simple average GPA in the
semester after the intervention with a dummy variable indicating whether
the participant was offered the summer program or not
(intention-to-treat analysis). We will also conduct the same regression
controlling for simple average GPA during the semester before the
intervention, gender, \& household income (an 8-point scale ranging from
1 = below \$20,000 and 8 = above \$150,000).
\end{quote}

\hypertarget{outliers-and-exclusions}{%
\subsection{Outliers and exclusions}\label{outliers-and-exclusions}}

\begin{quote}
Example 1: We will compute the overall mean and standard deviation
across all conditions, and winsorize at 2.5 SD above/below the mean.
Example 2: We will exclude participants who incorrectly answer at least
2 of our 3 attention check questions. Example 3: We will exclude any
participants who complete the survey in less than 30 seconds.
\end{quote}

\hypertarget{sample-size}{%
\subsection{Sample size}\label{sample-size}}

\begin{quote}
Example: We will offer the program until 500 people have agreed to
participate in it or until June 30, 2016 (whichever comes first).
\end{quote}

\hypertarget{other}{%
\subsection{Other}\label{other}}

\begin{quote}
Example: We will include a battery of questions for exploratory
purposes, including life satisfaction, amount of videogame playing, and
family activity. We will also provide an additional survey with 24
questions assessing achievement orientation. We will not report the
results of those analyses for the project being pre-registered. NOTE: If
you leave this blank it will read `Nothing else to pre-register.'
\end{quote}

\hypertarget{study-type}{%
\subsection{Study type}\label{study-type}}

Finally. For record keeping purposes, please tell us the type of study
you are pre-registering.

\begin{itemize}
\tightlist
\item
  Class project or assignment
\item
  Experiment
\item
  Survey
\item
  Observational/archival study
\item
  Other:
\end{itemize}

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{section}{%
\subsection{}\label{section}}

\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}

\noindent

\end{document}
