---
title: "My Project Manuscript"
author: "Andrew Vermey"
date: "30/09/2024"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Source: (Macher et al. 2024)

## Introduction
Welcome to my sample manuscript for my assignment. Here I took sample data on spotted gar sightings to use as a reference of my abilities. This manuscript will visually show some of this data and discuses the results. 

## My Data 
A table of my data

```{r load_data_full_path, echo=FALSE}
# Expand the file path to ensure R can interpret the "~" symbol
file_path <- path.expand("~/Desktop/Productivity-Course/00_rawdata/data.csv")

# Check if the file exists before loading
if (file.exists(file_path)) {
    loaded_data <- read.csv(file_path)
    
    # Check for empty column names
    if (any(colnames(loaded_data) == "")) {
        stop("Error: Empty column names in the dataset.")
    } else {
        # Display the summary if the data is loaded properly
        print(colnames(loaded_data))  # Print column names to check
        summary(loaded_data)
    }
} else {
    stop("Error: Data file not found!")
}
```


## Plot

```{r plot_data, echo=FALSE}
# Plotting the data
plot(loaded_data$time, loaded_data$value, type="l", xlab="Year", ylab="Spotted Gar Sightings")
```

As observed in the plot above, as time progressed the population of spotted gar gradually increased at a steady pace. Changes in seasonality impacted the populations, with winters showing a steady dip, and summers being the annual population peak.

